\singlespacing \vspace{-1.6cm} \LARGE Covariation among reproductive traits in flowering plants shape their interactions with pollinators

### 2023-02-28 Manuscript/Lanuza_et_al_2022.Rmd
Changing one word to british style

4. Our study identifies the major reproductive trait correlations in flowering plants and their role in shaping plant-pollinator interactions at a macro-ecological scale. These findings emphasize the importance of considering reproductive traits in the global spectrum of plant form and function, and the need to explore beyond floral morphological traits to broaden our understanding of plant-pollinator interactions.

>>>>

4. Our study identifies the major reproductive trait correlations in flowering plants and their role in shaping plant-pollinator interactions at a macro-ecological scale. These findings emphasise the importance of considering reproductive traits in the global spectrum of plant form and function, and the need to explore beyond floral morphological traits to broaden our understanding of plant-pollinator interactions.

### 2023-02-28 Manuscript/Lanuza_et_al_2022.tex
Changing one word to british style

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Globally, plants display enormous variation in life history strategies and trait combinations. However, evidence suggests that evolutionary and physiological constraints limit the number of plant ecological strategies. Although there have been recent advances in understanding correlations among plant traits, reproductive traits are rarely considered, despite their key role in shaping plant life-history strategies and interactions with pollinators.
\item
  Here, using a global dataset of 18 reproductive traits for 1,506 species, we investigate the reproductive spectrum of flowering plants to identify how it shapes interactions with pollinators.
\item
  We show that over 50\% of all trait variation is explained by the first two reproductive axes, which represent the negative correlation between flower number and flower size, and the negative correlation between autonomous selfing and floral display size. In addition, these reproductive axes were associated with different numbers of interacting partners and visitation rates of the distinct pollinator guilds. However, reproductive axes explain a relatively small amount of variance in pollinator interactions highlighting the need to incorporate other factors along with reproductive traits to fully explain large scale patterns of plant-pollinator interactions.
\item
  Our study identifies the major reproductive trait correlations in flowering plants and their role in shaping plant-pollinator interactions at a macro-ecological scale. These findings emphasize the importance of considering reproductive traits in the global spectrum of plant form and function, and the need to explore beyond floral morphological traits to broaden our understanding of plant-pollinator interactions.
\end{enumerate}

>>>>

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Globally, plants display enormous variation in life history strategies and trait combinations. However, evidence suggests that evolutionary and physiological constraints limit the number of plant ecological strategies. Although there have been recent advances in understanding correlations among plant traits, reproductive traits are rarely considered, despite their key role in shaping plant life-history strategies and interactions with pollinators.
\item
  Here, using a global dataset of 18 reproductive traits for 1,506 species, we investigate the reproductive spectrum of flowering plants to identify how it shapes interactions with pollinators.
\item
  We show that over 50\% of all trait variation is explained by the first two reproductive axes, which represent the negative correlation between flower number and flower size, and the negative correlation between autonomous selfing and floral display size. In addition, these reproductive axes were associated with different numbers of interacting partners and visitation rates of the distinct pollinator guilds. However, reproductive axes explain a relatively small amount of variance in pollinator interactions highlighting the need to incorporate other factors along with reproductive traits to fully explain large scale patterns of plant-pollinator interactions.
\item
  Our study identifies the major reproductive trait correlations in flowering plants and their role in shaping plant-pollinator interactions at a macro-ecological scale. These findings emphasise the importance of considering reproductive traits in the global spectrum of plant form and function, and the need to explore beyond floral morphological traits to broaden our understanding of plant-pollinator interactions.
\end{enumerate}
